
\documentclass[12pt]{amsart}
\usepackage{geometry} % see geometry.pdf on how to lay out the page. There's lots.
\geometry{a4paper} % or letter or a5paper or ... etc
\usepackage[T1]{fontenc}
\usepackage[latin9]{inputenc}
\usepackage{amsmath}
\usepackage{amsaddr}
\usepackage{hyperref}
\usepackage{dirtytalk}
\usepackage{float}
\usepackage{listings}
\usepackage{color}
\usepackage{tikz}


 
\definecolor{codegreen}{rgb}{0,0.6,0}
\definecolor{codegray}{rgb}{0.5,0.5,0.5}
\definecolor{stringcolor}{rgb}{0.7,0.23,0.36}
\definecolor{backcolour}{rgb}{0.95,0.95,0.92}
\definecolor{keycolor}{rgb}{0.007,0.01,1.0}
\definecolor{itemcolor}{rgb}{0.01,0.0,0.49}
 
\lstdefinestyle{mystyle}{
    %backgroundcolor=\color{backcolour},   
    commentstyle=\color{codegreen},
    keywordstyle=\color{keycolor},
    numberstyle=\tiny\color{codegray},
    stringstyle=\color{stringcolor},
    basicstyle=\footnotesize,
    breakatwhitespace=false,         
    breaklines=true,                 
    captionpos=b,                    
    keepspaces=true,                 
    numbers=left,                    
    numbersep=5pt,                  
    showspaces=false,                
    showstringspaces=false,
    showtabs=false,                  
    tabsize=2
}
 
\lstset{style=mystyle}

\lstdefinelanguage{Swift}{
  keywords={associatedtype, class, deinit, enum, extension, func, import, init, inout, internal, let, operator, private, protocol, public, static, struct, subscript, typealias, var, break, case, continue, default, defer, do, else, fallthrough, for, guard, if, in, repeat, return, switch, where, while, as, catch, dynamicType, false, is, nil, rethrows, super, self, Self, throw, throws, true, try, associativity, convenience, dynamic, didSet, final, get, infix, indirect, lazy, left, mutating, none, nonmutating, optional, override, postfix, precedence, prefix, Protocol, required, right, set, Type, unowned, weak, willSet},
  ndkeywords={class, export, boolean, throw, implements, import, this},
  sensitive=false,
  comment=[l]{//},
  morecomment=[s]{/*}{*/},
  morestring=[b]',
  morestring=[b]"
}

\lstset{emph={Int,count,abs,repeating,Array}, emphstyle=\color{itemcolor}}


\title{Week 05}

\date{\today}

\lstset{style=mystyle}

%%% BEGIN DOCUMENT
\begin{document}
\maketitle


Name: 
\\

Collaborators (if any): 


\section{Exercises/Problems}

\subsection{Sunny Day Studying} 
John has upcoming midterm exams and he needs needs to study. The weather has been warm and John would like to be outside more often. John enjoys being outside more when the weather is warmer: specifically, if the temperature is t integer units above zero, John's happiness will increase by t after spending the day outside (with a decrease in happiness when t is negative). On each of the n days until midterms, John will either study or hike outside (never both on the same day). In order to stay on top of coursework, John resolves never to hike outside more than two days in a row. Given a weather forecast estimating temperature for the next n days, describe an O(n)-time dynamic programming algorithm to determine which days John should study in order to increase happiness the most.  
\\

\subsection{Building Blocks} 
Emelyne's son Asher is a toddler who likes to build block towers. Each of his blocks is a 3D rectangular prism, where each block $b_i$ has a positive integer width $w_i$, height $h_i$, and length $l_i$, and he has at least three of each type of block. Asher can turn each block so that any face can serve as the top or bottom. The distance between the top and bottom face would be the height. Asher wants to construct a tower by stacking his blocks as high as possible, but he can only stack an oriented block $b_i$ on top of another oriented block $b_j$ if the dimensions of the bottom of block $b_i$ are strictly smaller than the dimensions of the top of block $b_j$ . Given the dimensions of each of his n blocks, describe an $O(n^2)$ -time algorithm to determine the height of the tallest tower Asher can build from his blocks. 
\\

Note- If the bottom of Asher's block $b_i$ has dimensions $m \times n$ and the top of block $b_j$ has dimensions $o \times p$, then Asher can stack $b_i$  on $b_j$ in this orientation if either: $m < o$ and $n < p$; or $m < p$ and $n < o$
\\


\end{document}
