
\documentclass[12pt]{amsart}
\usepackage{geometry} % see geometry.pdf on how to lay out the page. There's lots.
\geometry{a4paper} % or letter or a5paper or ... etc
\usepackage[T1]{fontenc}
\usepackage[latin9]{inputenc}
\usepackage{amsmath}
\usepackage{amsaddr}
\usepackage{hyperref}
\usepackage{dirtytalk}
\usepackage{float}
\usepackage{listings}
\usepackage{color}
\usepackage{tikz}
 
\definecolor{codegreen}{rgb}{0,0.6,0}
\definecolor{codegray}{rgb}{0.5,0.5,0.5}
\definecolor{stringcolor}{rgb}{0.7,0.23,0.36}
\definecolor{backcolour}{rgb}{0.95,0.95,0.92}
\definecolor{keycolor}{rgb}{0.007,0.01,1.0}
\definecolor{itemcolor}{rgb}{0.01,0.0,0.49}
 
\lstdefinestyle{mystyle}{
    %backgroundcolor=\color{backcolour},   
    commentstyle=\color{codegreen},
    keywordstyle=\color{keycolor},
    numberstyle=\tiny\color{codegray},
    stringstyle=\color{stringcolor},
    basicstyle=\footnotesize,
    breakatwhitespace=false,         
    breaklines=true,                 
    captionpos=b,                    
    keepspaces=true,                 
    numbers=left,                    
    numbersep=5pt,                  
    showspaces=false,                
    showstringspaces=false,
    showtabs=false,                  
    tabsize=2
}
 
\lstset{style=mystyle}

\lstdefinelanguage{Swift}{
  keywords={associatedtype, class, deinit, enum, extension, func, import, init, inout, internal, let, operator, private, protocol, public, static, struct, subscript, typealias, var, break, case, continue, default, defer, do, else, fallthrough, for, guard, if, in, repeat, return, switch, where, while, as, catch, dynamicType, false, is, nil, rethrows, super, self, Self, throw, throws, true, try, associativity, convenience, dynamic, didSet, final, get, infix, indirect, lazy, left, mutating, none, nonmutating, optional, override, postfix, precedence, prefix, Protocol, required, right, set, Type, unowned, weak, willSet},
  ndkeywords={class, export, boolean, throw, implements, import, this},
  sensitive=false,
  comment=[l]{//},
  morecomment=[s]{/*}{*/},
  morestring=[b]',
  morestring=[b]"
}

\lstset{emph={Int,count,abs,repeating,Array}, emphstyle=\color{itemcolor}}


\title{Week 03}

\date{\today}

\lstset{style=mystyle}

%%% BEGIN DOCUMENT
\begin{document}
\maketitle


Name: 
\\

Collaborators (if any): 

\section{Tasks}

\subsection{Sequence Rotations}

Here you can see a Sequence AVL Tree P. Perform the operation P.delete\_at(8) and draw the resulting tree after each rotation performed during the delete\_at operation. 

\begin{tikzpicture}[
    level 1/.style ={sibling distance=12em},
    level 2/.style ={sibling distance=6em},
    level 3/.style ={sibling distance=3em},
    every node/.style = {shape=circle,
    draw, align=center}]
]
    \node {6}
      child {
        node  {4}
            child {node {11}
            child {node {3}
            child {node {2}}
            child [missing]}
        child {node {1}}}
        child {node {5}
            child {node {9}}
            child [missing]}
      }
      child {
        node {12}
        child {node  {7}}
      child {node  {10}
        child {node  {8}} 
        child [missing]
        }
    };

    \end{tikzpicture}

\section{Exercises/Problems}

\subsection{Wild One} 
Emelyne has a wild 2 year old and she hears sounds of crashing and breaking and destruction coming from his playroom downstairs. She needs to decide whether to confront him (and be subject to his wrath and screaming) or to let him keep destroying things (which he seems to love to do these days). She decides to consult an elite group of n stuffed animals scattered around the room she's in currently. Emelyne surveys the animals and compiles a list of n polls, where each poll is a tuple matching a
different stuffed animals name with their integer opinion on the topic. Opinion + c means they are for
confronting her 2 year old, while opinion - c means they are against confronting her son. Emelyne wants to generate a list containing the names of the log n animals having the strongest opinions (breaking ties arbitrarily), so she can meet with them to discuss. For this problem, assume that the record containing the polls is read-only access controlled (the material in classified), so any computation must be written to alternative memory. 
\\

(a) Describe a O(n) time algorithm to generate Emelyne's list. 
\\

(b) Now suppose Emelyne's computer is only allowed to write to at most O(log n) space.
Describe an O(n log log n)-time algorithm to generate the list.

\end{document}
