
\documentclass[12pt]{amsart}
\usepackage{geometry} % see geometry.pdf on how to lay out the page. There's lots.
\geometry{a4paper} % or letter or a5paper or ... etc
\usepackage[T1]{fontenc}
\usepackage[latin9]{inputenc}
\usepackage{amsmath}
\usepackage{amsaddr}
\usepackage{hyperref}
\usepackage{dirtytalk}
\usepackage{float}
\usepackage{listings}
\usepackage{color}
 
\definecolor{codegreen}{rgb}{0,0.6,0}
\definecolor{codegray}{rgb}{0.5,0.5,0.5}
\definecolor{stringcolor}{rgb}{0.7,0.23,0.36}
\definecolor{backcolour}{rgb}{0.95,0.95,0.92}
\definecolor{keycolor}{rgb}{0.007,0.01,1.0}
\definecolor{itemcolor}{rgb}{0.01,0.0,0.49}
 
\lstdefinestyle{mystyle}{
    %backgroundcolor=\color{backcolour},   
    commentstyle=\color{codegreen},
    keywordstyle=\color{keycolor},
    numberstyle=\tiny\color{codegray},
    stringstyle=\color{stringcolor},
    basicstyle=\footnotesize,
    breakatwhitespace=false,         
    breaklines=true,                 
    captionpos=b,                    
    keepspaces=true,                 
    numbers=left,                    
    numbersep=5pt,                  
    showspaces=false,                
    showstringspaces=false,
    showtabs=false,                  
    tabsize=2
}
 
\lstset{style=mystyle}

\lstdefinelanguage{Swift}{
  keywords={associatedtype, class, deinit, enum, extension, func, import, init, inout, internal, let, operator, private, protocol, public, static, struct, subscript, typealias, var, break, case, continue, default, defer, do, else, fallthrough, for, guard, if, in, repeat, return, switch, where, while, as, catch, dynamicType, false, is, nil, rethrows, super, self, Self, throw, throws, true, try, associativity, convenience, dynamic, didSet, final, get, infix, indirect, lazy, left, mutating, none, nonmutating, optional, override, postfix, precedence, prefix, Protocol, required, right, set, Type, unowned, weak, willSet},
  ndkeywords={class, export, boolean, throw, implements, import, this},
  sensitive=false,
  comment=[l]{//},
  morecomment=[s]{/*}{*/},
  morestring=[b]',
  morestring=[b]"
}

\lstset{emph={Int,count,abs,repeating,Array}, emphstyle=\color{itemcolor}}


\title{Week 02}

\date{\today}

\lstset{style=mystyle}

%%% BEGIN DOCUMENT
\begin{document}
\maketitle


Name: 
\\

Collaborators (if any): 

\section{Tasks}

\subsection{Hash it out}

Insert integer keys C = [3, 18, 42, 31, 40, 56, 71] in order into a hash table of size
7 using the hash function h(k) = (8k + 2) mod 7. Collisions should be resolved via chaining,
where collisions are stored at the end of a chain. Draw a picture of the hash table after all keys
have been inserted (can insert a drawing into the PDF doc instead of writing syntax to create the drawing in LaTex).


\section{Exercises/Problems}
\subsection{Searching for Keys}
Emelyne is a busy mom who is on the hunt for her car keys. Unfortunately she has no idea which room her keys are in. Her house is composed of an infinite number of rooms, each identified by a unique positive integer. In each room in the house is an Amazon Alexa who can tell Emelyne whether or not her keys are in the room having a strictly higher room identifier than their own. Asking every Amazon Alexa in the house would take forever, and Emelyne wants to find her car keys quickly. Supposing
the keys are in room k, describe an algorithm to help Emelyne find her keys by talking to at most O(log k) Alexas. 

\subsection{Campus Construction} 
BYU-Idaho has employed Idaho Construction to build a new building on campus dedicated to cooking classes. BYU-I wants the new building be as tall as possible because each floor will be dedicated to a different cuisine of food. Rexburg zoning laws limit all new construction buildings to be no higher than height h, where h is a positive integer. Idaho Construction has decided to build the new building by stacking two giant aluminum cubes on top of each other. It's important to note, the aluminum cubes can only be made with a limited set of positive integer side lengths ${S = \{s_0, ..., s_{n-1}\}}$ Help the construction company purchase cubes for the new building.
\\

(a) Assuming the input S fits within $\Theta(n)$ machine words, describe an expected O(n)-
time algorithm to determine whether there exist a pair of side lengths in S that exactly
sum to h. 
\\

(b) Unfortunately for Idaho Construction, there is no pair of side lengths in S that sum exactly to h.
Assuming that $h = 800n^{8}$, describe a worst-case O(n)-time algorithm to return a pair
of side lengths in S whose sum is closest to h without going over. 


\end{document}