
\documentclass[12pt]{amsart}
\usepackage{geometry} % see geometry.pdf on how to lay out the page. There's lots.
\geometry{a4paper} % or letter or a5paper or ... etc
\usepackage[T1]{fontenc}
\usepackage[latin9]{inputenc}
\usepackage{amsmath}
\usepackage{amsaddr}
\usepackage{hyperref}
\usepackage{dirtytalk}
\usepackage{float}
\usepackage{listings}
\usepackage{color}
\usepackage{tikz}
\usepackage[shortlabels]{enumitem}

 
\definecolor{codegreen}{rgb}{0,0.6,0}
\definecolor{codegray}{rgb}{0.5,0.5,0.5}
\definecolor{stringcolor}{rgb}{0.7,0.23,0.36}
\definecolor{backcolour}{rgb}{0.95,0.95,0.92}
\definecolor{keycolor}{rgb}{0.007,0.01,1.0}
\definecolor{itemcolor}{rgb}{0.01,0.0,0.49}
 
\lstdefinestyle{mystyle}{
    %backgroundcolor=\color{backcolour},   
    commentstyle=\color{codegreen},
    keywordstyle=\color{keycolor},
    numberstyle=\tiny\color{codegray},
    stringstyle=\color{stringcolor},
    basicstyle=\footnotesize,
    breakatwhitespace=false,         
    breaklines=true,                 
    captionpos=b,                    
    keepspaces=true,                 
    numbers=left,                    
    numbersep=5pt,                  
    showspaces=false,                
    showstringspaces=false,
    showtabs=false,                  
    tabsize=2
}
 
\lstset{style=mystyle}

\lstdefinelanguage{Swift}{
  keywords={associatedtype, class, deinit, enum, extension, func, import, init, inout, internal, let, operator, private, protocol, public, static, struct, subscript, typealias, var, break, case, continue, default, defer, do, else, fallthrough, for, guard, if, in, repeat, return, switch, where, while, as, catch, dynamicType, false, is, nil, rethrows, super, self, Self, throw, throws, true, try, associativity, convenience, dynamic, didSet, final, get, infix, indirect, lazy, left, mutating, none, nonmutating, optional, override, postfix, precedence, prefix, Protocol, required, right, set, Type, unowned, weak, willSet},
  ndkeywords={class, export, boolean, throw, implements, import, this},
  sensitive=false,
  comment=[l]{//},
  morecomment=[s]{/*}{*/},
  morestring=[b]',
  morestring=[b]"
}

\lstset{emph={Int,count,abs,repeating,Array}, emphstyle=\color{itemcolor}}


\title{Week 10}

\date{\today}

\lstset{style=mystyle}

%%% BEGIN DOCUMENT
\begin{document}
\maketitle


Name: 
\\

Collaborators (if any): 

\section{Tasks}

\subsection{True or False}
Choose T or F for each of the following statements and briefly explain why.  
\begin{enumerate}
\item In a connected, weighted graph, every lowest weight edge is always in some minimum spanning tree. 
\item For a connected, weighted graph with n vertices and exactly n edges, it is possible to find a minimum spanning tree in O(n) time. 
\end{enumerate}

\section{Exercises/Problems}

\subsection{Longest Palindrome Sequence} 
In lecture 30, we discussed the longest palindrome sequence problem. Provide a function to compute the sequence. Experiment with various words to test your function. Example, given ''c h a r a c t e r'' , your function should output ''c a r a c''

\subsection{Procrastination}
You have N CSE 381 assignments due right now, but you haven't started any of them, so they are all going to be late. Each assignment requires $d_i$ days to complete, and has a cost penalty of $c_i$ per day. So if assignment $i$ ends up being finished $t$ days late, then it incurs a penalty of $t * ci$. Assume that once you start working on an assignment, you must work on it until you finish it, and that you cannot work on multiple assignments at the same time. 
\\

For example, suppose you have three assignments: A1 takes 3 days and has a penalty of 12 points/day, A2 takes 4 days and has a penalty of 20 points/day, and A3 takes 2 days and has
a penalty of 4 points/day. The best order is then A2, A1, A3 which results in a penalty of 20 * 4 + 12 * (4 + 3) + 4 * (3 + 4 + 2) = 200 points. 
\\

Give a greedy algorithm that outputs an ordering of the assignments that minimizes the total penalty for all the assignments. Analyze the running time and prove/discuss correctness. 
\end{document}
